---
author: "Liam Byrne"
date: "July 24, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### R Bridge - Week 2 Assignment:
*Implement code to calculate $\binom{n}{r} = \frac{n!}{(n-r)!-r!}$*

#### n_choose_r
The function checks that n and r are positive integers and that n > r. Outside of structuring the equation and checking for erroneous inputs, **calc_fact** will do most of the heavy lifting.

```{r tidy = TRUE}
n_choose_r <- function(n = 0, r = 0) {
    if (n != round(n) || r != round(r) || r < 0 || n < 0 || r > n) {
        return("Undefined: n & r must be positive integers and n must be greater than r")
    } else {
        return (calc_fact(n) / (calc_fact(n-r) * calc_fact(r)))
    }
}

```

#### calc_fact
The funciton uses recursion to calcualte the factorial of "n". Ideally, this should be a private funciton as it is assumed that **n_choose_r** is the one having access to it after having checked for possible errors in the input.
```{r}
calc_fact <- function(n) {
    if (n < 2) {
        return (1)
    } else {
        return (n * calc_fact(n - 1))
    }
}
```

#### Examples:
```{r}
# --------- Test Cases ---------
# r > n
n <- 3
r <- 52
sprintf("%s!/(%s-%s)!*%s! = %s.", n, n, r, r, n_choose_r(n,r))

# n < 0
n <- -52
r <- 3
sprintf("%s!/(%s-%s)!*%s! = %s.", n, n, r, r, n_choose_r(n,r))

# Combos of a five card hand
n <- 52
r <- 5
sprintf("%s!/(%s-%s)!*%s! = %s.", n, n, r, r, n_choose_r(n,r))

# Combos of creating a group of 5 out of 12 people
n <- 12
r <- 5
sprintf("%s!/(%s-%s)!*%s! = %s.", n, n, r, r, n_choose_r(n,r))
```

```{r}

```

